% !TEX encoding = UTF-8 Unicode
% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[a4paper, top=2.0cm, left=2.0cm, right=2.0cm, bottom=0cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{CJK}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}
\begin{CJK}{UTF8}{gbsn}

\begin{center}
{\LARGE \textbf{Zhanwei Wang (王占伟)}}

\vspace{0.4em}

(86) 138-1185-7720 
wangzw@wangzw.org
\end{center}

\vspace{-6mm}
\subsection*{Experience}
\vspace{-2mm}

\begin{itemize}
	\parskip=0.2mm

	\item
	\headerrow
		{\textbf{EMC Corporation / Pivotal Software Inc.}}
		{\textbf{Beijing, China}}
	\\
	\headerrow
		{\emph{Senior Member of Technical Staff}}
		{\emph{2011 -- present}}
	\begin{itemize*}
		\item Pivotal Software is a spin-out and joint venture of EMC Corporation and its subsidiary VMware that focus on cloud computing, big data and applications.
		
		\item Create HAWQ from Greenplum Database code base. 
		HAWQ is a massively parallel processing SQL engine sitting on top of HDFS. 
		As a hybrid of MPP database and Hadoop, it inherits the merits from both parties. 
		It adopts a layered architecture and relies on the distributed file system for data replication and fault tolerance. 
		In addition, it is standard SQL compliant and fully transactional.
		
		\item Design and implement the HDFS accessing module for HAWQ. 
		Provide the ability of efficiently accessing thousands of HDFS files concurrently. 
		Design the mechanism to avoid the data racing after the network partition.
		
		\item Design and implement the metadata dispatching module for HAWQ.
		Unlike Greenplum Database, 
		HAWQ segment is designed as stateless and not allowed to access the metadata to boost the scalability. 
		All metadata used by segments is collected by the master and dispatched to segments.
		
		\item Design and implement the transaction control module for HAWQ. 
		A novel and much simple transaction control mechanism is invented to boost the HAWQ scalability.
			
		\item Integrate HAWQ and HDFS security mechanism. 
		Design and implement an efficient way to query the data on security enabled HDFS.
		
		\item Implement basic functionalities of HAWQ such as creating, 
		dropping table, inserting, querying data and etc based on the new module and architecture design of HAWQ.

	\end{itemize*}

	\item
	\headerrow
		{\textbf{Beijing BaseSoft Information Technologies Inc.}}
		{\textbf{Beijing, China}}
	\\
	\headerrow
		{\emph{Software Engineer, Intern}}
		{\emph{2009 -- 2010}}
	\begin{itemize*}
		\item Kingbase is a famous database brand in China and used by  many domestic companies. 
		
		\item In charge of improving the database optimizer for complex query and improving TPCH benchmark test result. 
		By theoretical analysis and experimental testing, find out the problems and deficiencies of optimizer in the process of costs estimating. 
		Based on the public research results, design and implement the solution. 
		
		\item The score of TPCH test is improved almost 50\% and the execution time of some complex queries is reduced nearly 10 times.
	\end{itemize*}
	
	\item
	\headerrow
		{\textbf{Borqs International Holding Corp.}}
		{\textbf{Beijing, China}}
	\\
	\headerrow
		{\emph{Software Engineer, Intern}}
		{\emph{2008 -- 2009}}
	\begin{itemize*}
		\item Borqs is a hi-tech enterprise dedicated to providing end-to-end software solutions for the whole industrial chain of mobile communications. 
		
		\item Responsible for development of flash memory tools under windows platform. 
		Communicate with users, collect user requirements, reconstruct original tools. 
		Improve tools based on the feedback. 
		
		\item Improved the efficiency twice than that of the old one. These tools are widely used in development and smart phone manufacture in factory. 
	\end{itemize*}
\end{itemize}

\vspace{-8mm}
\subsection*{Open Source Project}
\vspace{-2mm}

\begin{itemize*}
	\parskip=0.2mm

	\item 
	\headerrow
		{\textbf{Libhdfs3}}
		{\textbf{http://pivotalrd.github.io/libhdfs3}}
	\\
	{\emph{A native C/\CPP\  HDFS client based on Apache Hadoop RPC protocol and HDFS data transfer protocol.}}
	
	\item 
	\headerrow
		{\textbf{CppStyle}}
		{\textbf{http://www.cppstyle.com}}
	\\
	{\emph{An Eclipse plugin that integrates clang-format and cpplint.py. Used to format C/\CPP\ code and check coding style.}}

\end{itemize*}

\vspace{-8mm}
\subsection*{Education}
\vspace{-2mm}

\begin{itemize*}
	\parskip=0.2mm

	\item 
	\headerrow
		{\textbf{Renmin University of China}}
		{\textbf{Beijing, China}}
	\\
	\headerrow
		{\emph{Master of Engineering, Computer Software \& Theory}}
		{\emph{2008 -- 2011}}

	\item 
	\headerrow
		{\textbf{Renmin University of China}}
		{\textbf{Beijing, China}}
	\\
	\headerrow
		{\emph{Bachelor of Engineering, Computer Science}}
		{\emph{2004 -- 2008}}

\end{itemize*}

\vspace{-8mm}
\subsection*{Publications}
\vspace{-2mm}

\begin{itemize*}
	\parskip=0.2mm

	\item 
	\headerrow
		{\textbf{HAWQ: a massively parallel processing SQL engine in Hadoop}}
		{\textbf{June, 2014}}
	\\
	{\emph{Proceedings of the 2014 ACM SIGMOD international conference on Management of data}}

\end{itemize*}

\vspace{-8mm}
\subsection*{Technical Skills}
\vspace{-2mm}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
	C, \CPP, Java, Python, shell script, SQL
	\item[Open Source Contributions:]
	Apache HDFS, Baidu sofa-pbrpc
	\item[Github:]
	https://github.com/wangzw
\end{description*}
\end{indentsection}

\end{CJK}
\end{document}
